---
title: Curriculum Vitae

format: 
  html:
    toc: true 
    theme:
      - colors.scss
      - multilingual-cv.scss
  pdf:
    pdf-engine: weasyprint
  
format-links: [pdf]

lightbox: true

execute:
  echo: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# Libraries
library(tidyverse)
library(knitr)
library(gt)
library(glue)
library(xtable)

# Dataset to use
dat <- read_csv("entries.csv")

# Publications
bib <-
  vitae::bibliography_entries("../bibliography/publications.bib") |>
  tibble::tibble() |>
  dplyr::mutate(issued = as.Date(issued))

bib <-
  rmarkdown::pandoc_citeproc_convert("../bibliography/publications.bib", type = "json") |>
  jsonlite::fromJSON(simplifyVector = TRUE) |>
  tibble() |>
  mutate(issued = eval(str2lang(as.character(issued)))) |>
  unnest_wider(issued, names_sep = "_") |>
  mutate(across(starts_with("issued_"), 
                       ~ if_else(is.na(.x), 1, .x))) |>
  mutate(date = paste0(issued_1, "-", issued_2, "-", issued_3) |>
                  as.Date()) |>
  mutate(authors = map(author, function(.x) {
    paste0(.x$family, ", ", .x$given) |>
      paste0(collapse = ", ")
  })) |>
  select(-author, -starts_with("issued"))
  
```

::: {.center}
# Anish S. Shah, MD, MS

[E-mail](mailto:ashah282@uic.edu) $\bullet$
[Website](https://shah-in-boots.github.io) $\bullet$
[Github](https://github.com/shah-in-boots) $\bullet$
[ORCID](https://orcid.org/0000-0002-9729-1558) $\bullet$
[Scholar](https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ)  
*Updated `r format(Sys.Date(), "%B %d, %Y")`*
:::

## Personal information

### Physical address

:::: {.columns}
::: {.column width="50%"}
_Office_

University of Illinois Chicago  
Division of Cardiology  
840 S Wood St  
Suite 920, M/C 715  
Chicago, IL 60612  
:::
::: {.column width="50%"}
_Clinic_

Jesse Brown VA Medical Center  
820 S. Damen Avenue  
Specialty Clinic, 2nd Floor, Damen Tower  
Chicago, IL 60612  
:::
::::


### Citizenship

United States of America

## Education

### Academic Training

**Bachelor of Science** -- Linguistics | Neuroscience [2007 -- 2011]{.cvdate}  
*Emory University College of Arts and Sciences*  

**Doctor of Medicine** [2012 -- 2016]{.cvdate}  
*Texas A&M University College of Medicine*  

**Master of Science** -- Clinical Research [2019 -- 2020]{.cvdate}  
*Emory University Laney Graduate School*  

### Clinical Training

**Residency** -- Internal Medicine [2016 -- 2019]{.cvdate}  
*J. Willis Hurst Internal Medicine Residency, Emory University School of Medicine*  

- Distinction in Teaching and Leadership

**Fellowship** -- Cardiovascular Medicine [2020 -- 2024]{.cvdate}  
*University of Illinois Chicago College of Medicine*

- Physician-Scientist Track
- Primary Mentor: Dawood Darbar, MD

**Fellowship** -- Clinical Cardiac Electrophysiology [2024 -- 2026]{.cvdate}  
*University of Utah School of Medicine*

## Appointments

**Postdoctoral Research Fellow** -- Epidemiology [2019 -- 2020]{.cvdate}  
*Emory University Rollins School of Public Health*  

- NIH-TL1 Scholar
- Primary Mentor: Amit J. Shah, MD, MS

**Assistant Professor of Medicine** -- Hospital Medicine [2019 -- 2020]{.cvdate}
*Division of Hospital Medicine, Emory University School of Medicine*

- Emory University Midtown Hospital
- Grady Memorial Hospital

**Instructor of Medicine** [2020 -- 2024]{.cvdate}  
*College of Medicine, University of Illinois Chicago*

## Publications

### Peer-Reviewed Publications

```{r}
bib |>
  filter(type == "article-journal")
```
