---
format: 
  html:
    toc: true 
    theme:
      - colors.scss
      - multilingual-cv.scss
  pdf:
    author: Anish S. Shah, MD, MS
    pdf-engine: weasyprint

css: pdf-cv.css
format-links: [pdf]

lightbox: true

execute:
  echo: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# Libraries
library(tidyverse)
library(knitr)
library(gt)
library(glue)

# Dataset to use
dat <- read_csv("entries.csv")

# Publications
bib <-
  rmarkdown::pandoc_citeproc_convert("publications.bib", type = "json") |>
  jsonlite::fromJSON(simplifyVector = TRUE) |>
  tibble() |>
  mutate(issued = eval(str2lang(as.character(issued)))) |>
  unnest_wider(issued, names_sep = "_") |>
  mutate(across(
    starts_with("issued_"),
    ~ if_else(is.na(.x), 1, .x)
  )) |>
  mutate(date = paste0(issued_1, "-", issued_2, "-", issued_3) |>
    as.Date()) |>
  # Handle authorship, bolding for me and asterisk for by mentees
  mutate(author = map(author, function(.d) {
    .d |>
      mutate(
        initials =
          str_extract_all(given, "\\b\\w") |>
            sapply(paste, collapse = "")
      )
  })) |>
  mutate(authors = map_chr(author, function(.x) {
    paste0(.x$family, ", ", .x$initials) |>
      paste0(collapse = ", ")
  })) |>
  mutate(authors = gsub("Shah, AS", "**Shah, AS**", authors)) |>
  select(
    -author,
    -starts_with("issued"),
    -starts_with("accessed"),
    -publisher,
    -abstract,
    -id,
    -ISSN,
    -keyword,
    -starts_with("collection"),
    -c("container-title-short")
  ) |> 
  arrange(date) |>
  rename(short_title = 'title-short',
         publication = 'container-title',
         meeting = event,
         location = 'event-place',
         url = URL,
         doi = DOI)
```

::: {.center}
# Anish S. Shah, MD, MS

[E-mail](mailto:ashah282@uic.edu) $\bullet$
[Website](https://shah-in-boots.github.io) $\bullet$
[Github](https://github.com/shah-in-boots) $\bullet$
[ORCID](https://orcid.org/0000-0002-9729-1558) $\bullet$
[Scholar](https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ)  
*Updated `r format(Sys.Date(), "%B %d, %Y")`*
:::

## Personal information

### Physical address

:::: {.columns}
::: {.column width="50%"}
_Office_

University of Illinois Chicago  
Division of Cardiology  
840 S Wood St  
Suite 920, M/C 715  
Chicago, IL 60612  
:::
::: {.column width="50%"}
_Clinic_

Jesse Brown VA Medical Center  
820 S. Damen Avenue  
Specialty Clinic, 2nd Floor, Damen Tower  
Chicago, IL 60612  
:::
::::


### Citizenship

United States of America

## Education

### Academic Training

**Bachelor of Science** -- Linguistics | Neuroscience [2007 -- 2011]{.cvdate}  
*Emory University College of Arts and Sciences*  

**Doctor of Medicine** [2012 -- 2016]{.cvdate}  
*Texas A&M University College of Medicine*  

**Master of Science** -- Clinical Research [2019 -- 2020]{.cvdate}  
*Emory University Laney Graduate School*  

### Clinical Training

**Residency** -- Internal Medicine [2016 -- 2019]{.cvdate}  
*J. Willis Hurst Internal Medicine Residency, Emory University School of Medicine*  

- Distinction in Teaching and Leadership

**Fellowship** -- Cardiovascular Medicine [2020 -- 2024]{.cvdate}  
*University of Illinois Chicago College of Medicine*

- Physician-Scientist Track
- Primary Mentor: Dawood Darbar, MD

**Fellowship** -- Clinical Cardiac Electrophysiology [2024 -- 2026]{.cvdate}  
*University of Utah School of Medicine*

## Appointments

**Postdoctoral Research Fellow** -- Epidemiology [2019 -- 2020]{.cvdate}  
*Emory University Rollins School of Public Health*  

- NIH-TL1 Scholar
- Primary Mentor: Amit J. Shah, MD, MS

**Assistant Professor of Medicine** -- Hospital Medicine [2019 -- 2020]{.cvdate}
*Division of Hospital Medicine, Emory University School of Medicine*

- Emory University Midtown Hospital
- Grady Memorial Hospital

**Instructor of Medicine** [2020 -- 2024]{.cvdate}  
*College of Medicine, University of Illinois Chicago*

## Publications

### Peer-Reviewed Publications

```{r articles, results="asis"}
articles <-
  bib |>
  filter(type == "article-journal") |>
  mutate(numbers = case_when(
    !is.na(issue) ~ paste0(volume, "(", issue, ")", ", ", page),
    is.na(issue) ~ paste0(volume, ", ", page),
  ))

glue_data(articles, "1. {authors} ({year(date)}). {title}. {title} {numbers}. DOI: {doi}")
```

### Software

```{r packages, results="asis"}
software <-
  bib |>
  filter(type == "software") |>
  # Fix formatting of titles
  mutate(
    title = sub("^Card", "card", title),
    title = sub("^Rmdl", "rmdl", title)
  )

glue_data(software, "1. {authors} ({year(date)}). {title}, Version: {version}. {url}")
```