---
format:
  html: default
  docx:
    notes-after-punctuation: true
  pdf:
    documentclass: article
    geometry:
      - top=10mm
      - left=10mm
      - right=10mm
      - bottom=10mm
      - heightrounded
    fontfamily: libertine
    colorlinks: true
    fontsize: "16"
    include-in-header:
      text: |
        \usepackage{multicol}
        \usepackage{lipsum}
        \usepackage{hyperref}
        \usepackage{wrapfig}
        \usepackage{libertine}
        \pagestyle{empty}
        
lightbox: true

engine: knitr

execute:
  echo: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(gt)
library(glue)

entries <- read_csv("entries.csv")

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

<!-- Title -->

::: {.content-visible when-format="pdf"}
\begin{huge}\begin{center}{\bf Anish S. Shah, MD, MS}\end{center}\end{huge}

\begin{center}
\href{mailto:ashah282@uic.edu}{E-mail} $\bullet$
\href{https:/shah-in-boots.github.io}{Website} $\bullet$
\href{https:/github.com/shah-in-boots}{Github} $\bullet$
\href{https://orcid.org/0000-0002-9729-1558}{ORCID} $\bullet$
\href{https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ}{Scholar}
\end{center}
:::

::: {.content-visible when-format="docx"}

# Anish S. Shah, MD, MS 

[E-mail](mailto:ashah282@uic.edu) $\bullet$
[Website](https://shah-in-boots.github.io) $\bullet$
[Github](https://github.com/shah-in-boots) $\bullet$
[ORCID](https://orcid.org/0000-0002-9729-1558) $\bullet$
[Scholar](https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ)

:::

::: {.content-visible when-format="html"}
# Anish S. Shah, MD, MS 

[{{< fa envelope >}}](mailto:ashah282@uic.edu) $\bullet$
[{{< fa brands github >}}](https://github.com/shah-in-boots) $\bullet$
[{{< fa brands orcid >}}](https://orcid.org/0000-0002-9729-1558) $\bullet$
[{{< fa brands google >}}](https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ) $\bullet$
[{{< fa globe >}}](https://shah-in-boots.github.io)  
:::

Last updated: `r format(Sys.Date(), "%B %d, %Y")`

---

## Personal information

### Physical address

_Office_

University of Illinois Chicago  
Division of Cardiology  
840 S Wood St  
Suite 920, M/C 715  
Chicago, IL 60612  

_Clinic_

Jesse Brown VA Medical Center  
820 S. Damen Avenue  
Specialty Clinic, 2nd Floor, Damen Tower  
Chicago, IL 60612  

### Citizenship

United States of America

## Education

### Academic Training

```{r}
#| label: education

# Filter and format the education section
education <-
  entries |>
  filter(section == "education") |>
  arrange(desc(end)) |>
  mutate(
    period = if_else(start == end, as.character(start), paste(start, "-", end)),
  ) |>
  select(period, title, institution, title, location, description) |>
  # Bold the main degrees
  mutate(title = paste0("__", title, "__")) |>
  # Combine multiple or duplicate descriptions
	# Make them italic
  group_by(title) |>
  mutate(description = if_else(
    !is.na(description),
    paste0("*", description, "*", collapse = "<br>"),
    description
  )) |>
  distinct() |>
  ungroup()

# GT table without a header
# Merges in the title and description on separate lines
gt(education) |>
  cols_merge(columns = c(title, description), pattern = "{1} {2}") |>
  cols_merge(columns = c(institution, location), pattern = "{1} {2}") |>
  fmt_missing(missing_text = "") |>
  fmt_markdown() |>
	tab_style(style = cell_text(size = "small"),
						locations = cells_body(columns = "institution")) |>
  tab_options(
    column_labels.hidden = TRUE,
    table.font.names = "Times New Roman",
    table.width = pct(100),
    data_row.padding = px(10),
    table.border.top.color = "white",
    table.border.bottom.color = "white",
    table.border.left.color = "white",
    table.border.right.color = "white"
  ) |>
  cols_width(
    period ~ pct(15),
    title ~ pct(50),
    institution ~ pct(35)
  )
```



### Postdoctoral Training

## Appointments

### Academic Appointments

### Clinical Appointments

## Professional Activities

### Professional Societies

### Service

Manuscript reviews

## Teaching and Mentoring

### Courses and Workshops

### Mentorship

### Lectures

## Invited Presentations

### Regional

### National

### International

- Academic mentorship
- Student would identify as a mentee

## Funding Support

## Honors and Awards

### Institutional/Regional

### National

### International

## Skills

### Clinical Skills

### Languages

### Technical Skills

### Certifications

## Conference Presentations

### Regional

### National

### International


## Bibliography

### Peer-Reviewed Publications

- Bold faculty name
- Asterisk by mentee name

### Manuscripts Accepted for Publication

### Manuscripts Submitted for Publication

### Books and Book Chapters

### Software 

### Case Reports
