---
format:
  html: default
  docx:
    notes-after-punctuation: true
  pdf:
    documentclass: article
    geometry:
      - top=10mm
      - left=10mm
      - right=10mm
      - bottom=10mm
      - heightrounded
    fontfamily: libertine
    colorlinks: true
    fontsize: "16"
    include-in-header:
      text: |
        \usepackage{multicol}
        \usepackage{lipsum}
        \usepackage{hyperref}
        \usepackage{wrapfig}
        \usepackage{libertine}
        \pagestyle{empty}
        
lightbox: true

engine: knitr

execute:
  echo: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(flextable)
entries <- read_csv("entries.csv")

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

<!-- Title -->

::: {.content-visible when-format="pdf"}
\begin{huge}\begin{center}{\bf Anish S. Shah, MD, MS}\end{center}\end{huge}

\begin{center}
\href{mailto:ashah282@uic.edu}{E-mail} $\bullet$
\href{https:/shah-in-boots.github.io}{Website} $\bullet$
\href{https:/github.com/shah-in-boots}{Github} $\bullet$
\href{https://orcid.org/0000-0002-9729-1558}{ORCID} $\bullet$
\href{https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ}{Scholar}
\end{center}
:::

::: {.content-visible when-format="docx"}

# Anish S. Shah, MD, MS 

[E-mail](mailto:ashah282@uic.edu) $\bullet$
[Website](https://shah-in-boots.github.io) $\bullet$
[Github](https://github.com/shah-in-boots) $\bullet$
[ORCID](https://orcid.org/0000-0002-9729-1558) $\bullet$
[Scholar](https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ)

:::

::: {.content-visible when-format="html"}
# Anish S. Shah, MD, MS 

[{{< fa envelope >}}](mailto:ashah282@uic.edu) $\bullet$
[{{< fa brands github >}}](https://github.com/shah-in-boots) $\bullet$
[{{< fa brands orcid >}}](https://orcid.org/0000-0002-9729-1558) $\bullet$
[{{< fa brands google >}}](https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ) $\bullet$
[{{< fa globe >}}](https://shah-in-boots.github.io)  
:::

Last updated: `r format(Sys.Date(), "%B %d, %Y")`

---

## Personal information

### Physical address

_Office_

University of Illinois Chicago  
Division of Cardiology  
840 S Wood St  
Suite 920, M/C 715  
Chicago, IL 60612  

_Clinic_

Jesse Brown VA Medical Center  
820 S. Damen Avenue  
Specialty Clinic, 2nd Floor, Damen Tower  
Chicago, IL 60612  

### Citizenship

United States of America

## Education

### Academic Training

```{r}
#| label: education

# Load the CSV file
entries <- read_csv("entries.csv")

# Filter and display the education section
education <- entries |>
  filter(section == "education") |>
  select(start, end, title, institution, description) |>
  mutate(period = if_else(start == end, as.character(start), paste(start, "-", end))) |>
  replace_na(list(start = "", end = "", title = "", institution = "", description = "", period = ""))

# Conditionally render based on the output format
if (knitr::is_latex_output()) {
  # LaTeX table for PDF output
  kable(education |>
          select(period, title, institution, description),
        format = "latex", booktabs = TRUE, escape = FALSE, col.names = c("Period", "Degree", "Institution", "Description")) |>
    kable_styling(latex_options = c("striped", "hold_position", "scale_down")) |>
    column_spec(1, bold = TRUE) |>
    column_spec(2, width = "3cm") |>
    column_spec(3, width = "4cm") |>
    column_spec(4, width = "7cm")
} else if (knitr::pandoc_to("html")) {
  # HTML table for HTML output
  kable(education |>
          select(period, title, institution, description),
        format = "html", table.attr = "class='table table-striped'", col.names = c("Period", "Degree", "Institution", "Description")) |>
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
} else if (knitr::pandoc_to("docx")) {
  # Flextable for Word output
  flextable(education |>
              select(period, title, institution, description)) |>
    set_header_labels(period = "Period", title = "Degree", institution = "Institution", description = "Description") |>
    theme_vanilla() |>
    autofit()
}

```

### Postdoctoral Training

## Appointments

### Academic Appointments

### Clinical Appointments

## Professional Activities

### Professional Societies

### Service

Manuscript reviews

## Teaching and Mentoring

### Courses and Workshops

### Mentorship

### Lectures

## Invited Presentations

### Regional

### National

### International

- Academic mentorship
- Student would identify as a mentee

## Funding Support

## Honors and Awards

### Institutional/Regional

### National

### International

## Skills

### Clinical Skills

### Languages

### Technical Skills

### Certifications

## Conference Presentations

### Regional

### National

### International


## Bibliography

### Peer-Reviewed Publications

- Bold faculty name
- Asterisk by mentee name

### Manuscripts Accepted for Publication

### Manuscripts Submitted for Publication

### Books and Book Chapters

### Software 

### Case Reports
