---
format: 
  html:
    theme:
      - colors.scss
  docx:
    notes-after-punctuation: true
    reference-doc: reference.docx
  pdf: 
    pdf-engine: weasyprint

lightbox: true

engine: knitr

execute:
  echo: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# Libraries
library(tidyverse)
library(knitr)
library(kableExtra)
library(gt)
library(glue)

# Dataset to use
dat <- read_csv("entries.csv") 
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# Libraries
library(tidyverse)
library(knitr)
library(kableExtra)
library(gt)
library(glue)

# Dataset to use
dat <- read_csv("entries.csv") 
```

# Anish S. Shah, MD, MS 

[{{< fa envelope >}}](mailto:ashah282@uic.edu) $\bullet$
[{{< fa brands github >}}](https://github.com/shah-in-boots) $\bullet$
[{{< fa brands orcid >}}](https://orcid.org/0000-0002-9729-1558) $\bullet$
[{{< fa brands google >}}](https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ) $\bullet$
[{{< fa globe >}}](https://shah-in-boots.github.io)  
:::

Last updated: `r format(Sys.Date(), "%B %d, %Y")`

## Personal information

### Physical address

_Office_

University of Illinois Chicago  
Division of Cardiology  
840 S Wood St  
Suite 920, M/C 715  
Chicago, IL 60612  

_Clinic_

Jesse Brown VA Medical Center  
820 S. Damen Avenue  
Specialty Clinic, 2nd Floor, Damen Tower  
Chicago, IL 60612  

### Citizenship

United States of America

## Education

### Academic Training

```{r}
education <-
  dat |>
  filter(section == "education") |>
  arrange(desc(end)) |>
  mutate(
    period = if_else(start == end, as.character(start), paste(start, "-", end)),
  ) |>
  select(period, title, institution, title, location, description) 

# GT table without a header
# Merges in the title and description on separate lines
educationTable <-
	gt(education) |>
  cols_merge(columns = c(title, description), pattern = "{1} {2}") |>
  cols_merge(columns = c(institution, location), pattern = "{1} {2}") |>
  sub_missing(missing_text = "") |>
  fmt_markdown() |>
	tab_style(style = cell_text(size = "small"),
						locations = cells_body(columns = "institution")) |>
  tab_options(
    column_labels.hidden = TRUE,
    table.font.names = "Times New Roman",
    table.width = pct(100),
    data_row.padding = px(10),
    table.border.top.color = "white",
    table.border.bottom.color = "white",
    table.border.left.color = "white",
    table.border.right.color = "white"
  ) |>
  cols_width(
    period ~ pct(15),
    title ~ pct(50),
    institution ~ pct(35)
  ) 

educationTable
```