---
format: 
  html:
    toc: true 
    theme:
      - colors.scss
      - multilingual-cv.scss
  pdf:
    author: Anish S. Shah, MD, MS
    pdf-engine: weasyprint

css: pdf-cv.css
format-links: [pdf]

lightbox: true

execute:
  echo: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# Libraries
library(tidyverse)
library(knitr)
library(gt)
library(glue)

# Dataset to use
dat <- read_csv("entries.csv")

# Publications
bib <-
  rmarkdown::pandoc_citeproc_convert("../bibliography/publications.bib", type = "json") |>
  jsonlite::fromJSON(simplifyVector = TRUE) |>
  tibble() |>
  janitor::clean_names() |>
  mutate(issued = eval(str2lang(as.character(issued)))) |>
  unnest_wider(issued, names_sep = "_") |>
  mutate(across(
    starts_with("issued_"),
    ~ if_else(is.na(.x), 1, .x)
  )) |>
  mutate(date = paste0(issued_1, "-", issued_2, "-", issued_3) |>
    as.Date()) |>
  # Handle authorship, bolding for me and asterisk for by mentees
  mutate(author = map(author, function(.d) {
    .d |>
      mutate(
        initials =
          str_extract_all(given, "\\b\\w") |>
            sapply(paste, collapse = "")
      )
  })) |>
  mutate(authors = map_chr(author, function(.x) {
    paste0(.x$family, ", ", .x$initials) |>
      paste0(collapse = ", ")
  })) |>
  mutate(authors = gsub("Shah, AS", "**Shah, AS**", authors)) |>
  # Adjust publication locations and meeting locations
  mutate(location = case_when(
    !is.na(event_place) ~ event_place,
    !is.na(publisher_place) ~ publisher_place,
    TRUE ~ NA
  )) |>
  rename(journal = container_title,
         journal_short = container_title_short,
         meeting = event) |> 
  select(
    -author,
    -starts_with("issued"),
    -starts_with("accessed"),
    -abstract,
    -id,
    -issn,
    -keyword,
    -event_place,
    -publisher_place,
    -collection_title,
    -language
  ) |> 
  arrange(date) 
```

::: {.center}
# Anish S. Shah, MD, MS

[E-mail](mailto:ashah282@uic.edu) $\bullet$
[Website](https://shah-in-boots.github.io) $\bullet$
[Github](https://github.com/shah-in-boots) $\bullet$
[ORCID](https://orcid.org/0000-0002-9729-1558) $\bullet$
[Scholar](https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ)  
*Updated `r format(Sys.Date(), "%B %d, %Y")`*
:::

## Personal information

### Physical address

:::: {.columns}
::: {.column width="50%"}
_Office_

University of Illinois Chicago  
Division of Cardiology  
840 S Wood St  
Suite 920, M/C 715  
Chicago, IL 60612  
:::
::: {.column width="50%"}
_Clinic_

Jesse Brown VA Medical Center  
820 S. Damen Avenue  
Specialty Clinic, 2nd Floor, Damen Tower  
Chicago, IL 60612  
:::
::::


### Citizenship

United States of America

## Education

### Academic Training

**Bachelor of Science** -- Linguistics | Neuroscience [2007 -- 2011]{.cvdate}  
*Emory University College of Arts and Sciences*  

**Doctor of Medicine** [2012 -- 2016]{.cvdate}  
*Texas A&M University College of Medicine*  

**Master of Science** -- Clinical Research [2019 -- 2020]{.cvdate}  
*Emory University Laney Graduate School*  

### Clinical Training

**Residency** -- Internal Medicine [2016 -- 2019]{.cvdate}  
*J. Willis Hurst Internal Medicine Residency, Emory University School of Medicine*  

- Distinction in Teaching and Leadership

**Fellowship** -- Cardiovascular Medicine [2020 -- 2024]{.cvdate}  
*University of Illinois Chicago College of Medicine*

- Physician-Scientist Track
- Primary Mentor: Dawood Darbar, MD

**Fellowship** -- Clinical Cardiac Electrophysiology [2024 -- 2026]{.cvdate}  
*University of Utah School of Medicine*

## Certification

American Board of Internal Medicine Certification  
Cardiology Boards
Echo boards

## Appointments

**Postdoctoral Research Fellow** -- Epidemiology [2019 -- 2020]{.cvdate}  
*Emory University Rollins School of Public Health*  

- NIH-TL1 Scholar
- Primary Mentor: Amit J. Shah, MD, MS

**Assistant Professor of Medicine** -- Hospital Medicine [2019 -- 2020]{.cvdate}
*Division of Hospital Medicine, Emory University School of Medicine*

- Service Lines: Hospital Medicine, Procedure Service
- Locations: Grady Memorial Hospital, Emory University Midtown Hospital

**Instructor of Medicine** [2020 -- 2024]{.cvdate}  
*College of Medicine, University of Illinois Chicago*


## Honors and Awards

### Local

Delores B. Aldridge Excellence in Service to a Diverse Community Award [2009]{.cvdate}  
*Emory University*

Speaker to His Holiness the XIV Dalai Lama [2009]{.cvdate}  
*Emory-Tibet Science Initiative* 

- Selected to represent Emory students in a meeting with the 14th Dalai Lama in MacLeod Gange, India.

Nu Rho Psi Honor Society [2009 -- 2011]{.cvdate}  
*Emory University*

College of Medicine Research Symposium [2015]{.cvdate}   
*Texas A&M University* 

- $1^{st}$ Place Oral Presentation

### Regional

Doctor’s Dilemma (Medical Jeopardy) [2017]{.cvdate}  
*Georgia American College of Physician Conference*

### National

EMT-Basic National Competition [2007]{.cvdate}
*Health Occupation Students of America*

- $1^{st}$ Place

Medical Student Research Program in Diabetes [2013]{.cvdate}  
*National Institute of Diabetes and Digestive and Kidney Diseases*

American Heart Association Scientific Sessions - Top Donors Meeting Presentation [2018]{.cvdate}  

- Special invitation to discuss research with AHA leadership and top philanthropists
	
NIH-TL1 Postdoctoral Fellow [2019-2020]{.cvdate}  
*Ruth L. Kirschtein National Research Service Award*

NIH-T32 Postdoctoral Fellow [2019-2020]{.cvdate}  
*Ruth L. Kirschtein National Research Service Award*

NIH-F32 Postdoctoral Fellow [2021-2024]{.cvdate}  
*Ruth L. Kirschtein National Research Service Award*

### International

Atrial Fibrillation Genetics Consortium Fellow [2023 -- 2024]{.cvdate}
*Atrial Fibrillation Genetics Consortium*

## Professional Activities

### Professional Societies

Texas Medical Association [2012 -- 2016]{.cvdate}  
*Student Member*

American College of Physicians [2012 -- Present]{.cvdate}  
*Member*

American Medical Aossciation [2012 -- Present]{.cvdate}   
*Member*

American Heart Association [2018 -- Present]{.cvdate}  
*Fellow-In-Training*

American College of Cardiology [2020 -- Present]{.cvdate}  
*Fellow-In-Training*

Heart Rhythm Society [2023 -- Present]{.cvdate}  
*Fellow-In-Training*

### Service

BMJ Open Diabetes Research & Care [2019]{.cvdate}  
*Ad-Hoc Reviewer*

Journal of Electroconvulsive Therapy [2020]{.cvdate}  
*Ad-Hoc Reviewer*

Journal of Cardiovascular Electrophysiology [2021]{.cvdate}
*Ad-Hoc Reviewer*

BMJ Open [2021]{.cvdate}
*Ad-Hoc Reviewer*

Circulation: Arrhythmia and Electrophysiology [2023]{.cvdate}
*Ad-Hoc Reviewer*

Applied Psychophysiology and Biofeedback [2024]{.cvdate}  
*Ad-Hoc Reviewer*

BMC Global and Public Health [2024]{.cvdate}  
*Ad-Hoc Reviewer*

## Teaching and Mentoring

### Courses and Workshops

### Mentorship

### Lectures

## Invited Presentations

### Regional

### National

### International

- Academic mentorship
- Student would identify as a mentee

## Publications

### Peer-Reviewed Publications

```{r articles, results="asis"}
articles <-
  bib |>
  filter(type == "article-journal") |>
  mutate(numbers = case_when(
    !is.na(issue) ~ paste0(volume, "(", issue, ")", ", ", page),
    is.na(issue) ~ paste0(volume, ", ", page),
  ))

glue_data(articles, "1. {authors} ({year(date)}). {title}. {journal} {numbers}. doi:[{doi}](https://doi.org/{doi})")
```

### Working Manuscripts

```{r manuscripts, results="asis"}
manuscripts <-
  bib |>
  filter(type == "manuscript") 

glue_data(manuscripts, "1. {authors} ({year(date)}). {title}.")
```

### Monographs

```{r thesis, results="asis"}
thesis <-
  bib |>
  filter(type == "thesis") 

glue_data(thesis, "1. {authors} ({year(date)}). '{title}'. Master's Thesis. {publisher}. [{url}]({url})")
```

### Software

```{r software, results="asis"}
software <-
  bib |>
  filter(type == "software") |>
  # Fix formatting of titles
  mutate(
    title = sub("^Card", "card", title),
    title = sub("^Rmdl", "rmdl", title)
  )

glue_data(software, "1. {authors} ({year(date)}). {title}, Version: {version}. [{url}]({url})")
```

### Conference Proceedings

```{r abstracts, results="asis"}
abstracts <-
  bib |>
  filter(type == "paper-conference") |>
  mutate(numbers = case_when(
    !is.na(issue) ~ paste0(volume, "(", issue, ")", ", ", page),
    is.na(issue) ~ paste0(volume, ", ", page),
  ))

glue_data(abstracts, "1. {authors} ({year(date)}). {title}. {meeting}, {date}, {location}. In: {journal} {numbers}. doi:doi:[{doi}](https://doi.org/{doi})")
```