---
format: 
  html:
    toc: true 
    theme:
      - colors.scss
      - multilingual-cv.scss
  pdf:
    author: Anish S. Shah, MD, MS
    pdf-engine: weasyprint

css: pdf-cv.css
format-links: [pdf]

lightbox: true

execute:
  echo: false
  cache: false
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# Libraries
library(tidyverse)
library(knitr)
library(gt)
library(glue)

# Dataset to use
dat <- read_csv("entries.csv")

# Publications
#   Publisher is company or institution, but there are exceptions
#   Exceptions include when is manuscript (unpublished)
#   Then, options are: 1) draft, 2) rip
bib <-
  rmarkdown::pandoc_citeproc_convert("../bibliography/publications.bib", type = "json") |>
  jsonlite::fromJSON(simplifyVector = TRUE) |>
  tibble() |>
  janitor::clean_names() |>
  mutate(issued = eval(str2lang(as.character(issued)))) |>
  unnest_wider(issued, names_sep = "_") |>
  mutate(across(
    starts_with("issued_"),
    ~ if_else(is.na(.x), 1, .x)
  )) |>
  mutate(date = paste0(issued_1, "-", issued_2, "-", issued_3) |>
    as.Date()) |>
  # Handle authorship, bolding for me and asterisk for by mentees
  mutate(author = map(author, function(.d) {
    .d |>
      mutate(
        initials =
          str_extract_all(given, "\\b\\w") |>
            sapply(paste, collapse = "")
      )
  })) |>
  mutate(authors = map_chr(author, function(.x) {
    paste0(.x$family, ", ", .x$initials) |>
      paste0(collapse = ", ")
  })) |>
  mutate(authors = gsub("Shah, AS", "**Shah, AS**", authors)) |>
  # Adjust publication locations and meeting locations
  mutate(location = case_when(
    !is.na(event_place) ~ event_place,
    !is.na(publisher_place) ~ publisher_place,
    TRUE ~ NA
  )) |>
  rename(
    journal = container_title,
    journal_short = container_title_short,
    meeting = event
  ) |>
  select(
    -author,
    -starts_with("issued"),
    -starts_with("accessed"),
    -abstract,
    -id,
    -issn,
    -keyword,
    -event_place,
    -publisher_place,
    -collection_title,
    -language
  ) |>
  arrange(date)

# Mentees
# The mentorship section should include any people you are or have been mentoring. When deciding who to include, consider whether you could readily describe the skills, knowledge, insights, or value you have provided to the mentee. This section should include their name, length of mentorship, current role (e.g., faculty role, fellow, resident, medical student), and institution as well as their prior role when you began mentoring them (if applicable). As not all institutional CV formats have a designated location for this, you could consider making this a separate appendix file.
mentees <- read_csv("mentees.csv")
```

::: {.center}
# Anish S. Shah, MD, MS

[E-mail](mailto:ashah282@uic.edu) $\bullet$
[Website](https://shah-in-boots.github.io) $\bullet$
[Github](https://github.com/shah-in-boots) $\bullet$
[ORCID](https://orcid.org/0000-0002-9729-1558) $\bullet$
[Scholar](https://scholar.google.com/citations?hl=en&user=jFGiIJMAAAAJ)  
*Updated `r format(Sys.Date(), "%B %d, %Y")`*
:::

## Personal information

### Physical address

:::: {.columns}
::: {.column width="50%"}
_Office_

University of Utah  
Division of Cardiology   
30 North Mario Capecchi Drive  
3rd Floor North  
Salt Lake City, UT 84112  
:::
::: {.column width="50%"}
_Clinic_

George E. Wahlen VA Medical Center  
500 Foothill Drive  
Building 1, 2nd Floor  
Salt Lake City, UT 84148  
:::
::::


### Citizenship

United States of America

## Education

### Academic Training

**Bachelor of Science** -- Linguistics | Neuroscience [2007 -- 2011]{.cvdate}  
*Emory University College of Arts and Sciences*  

**Doctor of Medicine** [2012 -- 2016]{.cvdate}  
*Texas A&M University College of Medicine*  

**Master of Science** -- Clinical Research [2019 -- 2020]{.cvdate}  
*Emory University Laney Graduate School*  

### Clinical Training

**Residency** -- Internal Medicine [2016 -- 2019]{.cvdate}  
*J. Willis Hurst Internal Medicine Residency, Emory University School of Medicine*  

- Distinction in Teaching and Leadership

**Fellowship** -- Cardiovascular Medicine [2020 -- 2024]{.cvdate}  
*University of Illinois Chicago College of Medicine*

- Physician-Scientist Track
- Primary Mentor: Dawood Darbar, MD

**Fellowship** -- Clinical Cardiac Electrophysiology [2024 -- 2026]{.cvdate}  
*University of Utah School of Medicine*

## Skills 

### Clinical Skills

Point-of-care ultrasonography   
Arterial line placement (radial, brachial, dorsalis pedis)  
Arthrocentesis (knee, ankle, shoulder)  
Central line placement (internal jugular, femoral, subclavian)  
Lumbar puncture  
Thoracentesis  
Paracentesis  
Coronary angiography  
Temporary/permanent pacemaker implantation  
Echocardiography - 2D/3D, transthoracic and transesophageal

### Languages

- English -- fluent
- Gujurati -- fluent
- Spanish -- fluent

### Technical Skills

`R` - programming language for statistical computing  
`PERL` - high-level programming language for text processing and manipulation  
`C++` - low-level programming language for data processing  
`Vim` - command line editing   
`Git` - version control system   
`MATLAB` - matrix-oriented mathematical programming language   
`Python` - high-level programming language for data analysis  

### Certifications

Emergency Medical Technician Basic [2007 -- 2010]{.cvdate}
*National Registry of Emergency Medical Technicians*

Basic Life Support [2012 -- Present]{.cvdate}  
*American Heart Association*

Advanced Cardiovascular Life Support [2012 -- Present]{.cvdate}  
*American Heart Association*

Advanced Trauma Life Support [2012 -- 2016]{.cvdate}
*American College of Surgeons*

Open Water Diver [2015 -- Present]{.cvdate}  
*Professional Association of Diving Instructors*

Wilderness First Responder [2016 -- Present]{.cvdate}
*National Outdoor Leadership School*

Basic Keelboat 101 [2017 -- Present]{.cvdate}  
*American Sailing Association*

Internal Medicine [2019 -- Present]{.cvdate}  
*American Board of Internal Medicine*

Adult Echocardiography [2023 -- Present]{.cvdate}  
*National Board of Echocardiography*

Cardiovascular Medicine [2023 -- Present]{.cvdate}  
*American Board of Internal Medicine*

## Appointments

**Postdoctoral Research Fellow** -- Epidemiology [2019 -- 2020]{.cvdate}  
*Emory University Rollins School of Public Health*  

- NIH-TL1 Scholar
- Primary Mentor: Amit J. Shah, MD, MS

**Assistant Professor of Medicine** [2019 -- 2020]{.cvdate}  
*Division of Hospital Medicine, Emory University School of Medicine*

- Service Lines: Hospital Medicine, Procedure Service
- Locations: Grady Memorial Hospital, Emory University Midtown Hospital

**Instructor of Medicine** [2020 -- 2024]{.cvdate}  
*College of Medicine, University of Illinois Chicago*

## Honors and Awards

### Local

Delores B. Aldridge Excellence in Service to a Diverse Community Award [2009]{.cvdate}  
*Emory University*

Speaker to His Holiness the XIV Dalai Lama [2009]{.cvdate}  
*Emory-Tibet Science Initiative* 

- Selected to represent Emory students in a meeting with the 14th Dalai Lama in MacLeod Gange, India.

Nu Rho Psi Honor Society [2009 -- 2011]{.cvdate}  
*Emory University*

College of Medicine Research Symposium [2015]{.cvdate}   
*Texas A&M University* 

- $1^{st}$ Place Oral Presentation

### Regional

Doctor’s Dilemma (Medical Jeopardy) [2017]{.cvdate}  
*Georgia American College of Physician Conference*

### National

EMT-Basic National Competition [2007]{.cvdate}
*Health Occupation Students of America*

- $1^{st}$ Place

Medical Student Research Program in Diabetes [2013]{.cvdate}  
*National Institute of Diabetes and Digestive and Kidney Diseases*

American Heart Association Scientific Sessions - Top Donors Meeting Presentation [2018]{.cvdate}  

- Special invitation to discuss research with AHA leadership and top philanthropists
	
NIH-TL1 Postdoctoral Fellow [2019-2020]{.cvdate}  
*Ruth L. Kirschtein National Research Service Award*

NIH-T32 Postdoctoral Fellow [2019-2020]{.cvdate}  
*Ruth L. Kirschtein National Research Service Award*

NIH-F32 Postdoctoral Fellow [2021-2024]{.cvdate}  
*Ruth L. Kirschtein National Research Service Award*

### International

Atrial Fibrillation Genetics Consortium Fellow [2023 -- 2024]{.cvdate}  
*Atrial Fibrillation Genetics Consortium*

## Professional Activities

### Professional Societies

Texas Medical Association [2012 -- 2016]{.cvdate}  
*Student Member*

American College of Physicians [2012 -- Present]{.cvdate}  
*Member*

American Medical Aossciation [2012 -- Present]{.cvdate}   
*Member*

American Heart Association [2018 -- Present]{.cvdate}  
*Fellow-In-Training*

American College of Cardiology [2020 -- Present]{.cvdate}  
*Fellow-In-Training*

Heart Rhythm Society [2023 -- Present]{.cvdate}  
*Fellow-In-Training*

### Service

*Ad-Hoc Reviewer*:  

BMJ Open Diabetes Research & Care [2019]{.cvdate}  
Journal of Electroconvulsive Therapy [2020]{.cvdate}  
Journal of Cardiovascular Electrophysiology [2021]{.cvdate}  
BMJ Open [2021]{.cvdate}  
Circulation: Arrhythmia and Electrophysiology [2023]{.cvdate}  
American Journal of Cardiology [2022-2023]{.cvdate}
Applied Psychophysiology and Biofeedback [2024]{.cvdate}  
BMC Global and Public Health [2024]{.cvdate}   

## Teaching and Mentoring Activities

### Preceptorship

Teaching Assistant -- Cellular Biology [2010]{.cvdate}  
*Department of Biology, Emory University College of Arts and Sciences*

Tutor -- Biology, Chemistry, Physics [2011 -- 2012]{.cvdate}  
*Department of Physics, North Lake College*

Tutor -- Histology [2013]{.cvdate}   
*Texas A&M University College of Medicine*

Faculty Preceptor -- Physician Assistant Program [2017 -- 2019]{.cvdate}  
*Didactic Experiential Learning Program, Emory University School of Medicine*

Teaching Attending -- Point-of-Care Ultrasound Elective [2019 -- 2020]{.cvdate}  
*J. Willis Hurst Internal Medicine Residency Program, Emory University School of Medicine*

### Workshops

Session Leader -- Internship Bootcamp [2016]{.cvdate}  
*Texas A&M University College of Medicine*

Workshop Leader -- M3 Ultrasound Workshop [2018 -- 2019]{.cvdate}  
*Emory University School of Medicine*

Workshop Leader -- Physical Exam and Clinical Decision Making [2019]{.cvdate}  
*Emory University School of Medicine*

Workshop Leader -- Point-of-Care Ultrasound Workshop [2018]{.cvdate}  
*Southern Hospital Medicine Conference*

### Clinical Presentations

*Emory University*:

Bite-Sized Teaching Mode: Lotions, Ointments, and Creams, Oh My! [February 28, 2018]{.cvdate}  
Journal Club: Intervention for Ischemic Stroke [March 21, 2018]{.cvdate}  
Bite-Sized Teaching Mode: Ironing Out Transfusions in Sickle Cell [September 26, 2018]{.cvdate}

*University of Illinois Chicago*:

Clinical Case Conference: Restrictive Cardiomyopathy [December 20, 2020]{.cvdate}  
Journal Club: GALACTIC-HF [February 1, 2021]{.cvdate}  
Cardiac Catheterization Conference: Antiplatelet Agents [November 16, 2021]{.cvdate}  
Electrophysiology Conference: Typical AVNRT [December 7, 2022]{.cvdate}  
Echocardiography Conference: Hypertrophic Cardiomyopathy [February 23, 2023]{.cvdate}   
Clinical Case Conference: Dilated Cardiomyopathy [April 8, 2024]{.cvdate}   

### Mentorship

```{r mentees, results="asis"}
dat <- 
	mentees |>
	arrange(start) |>
  mutate(end = as.character(end)) |>
  mutate(end = if_else(is.na(end), "Present", end)) |>
  mutate(notes = gsub(", ", "<br>", notes))

glue_data(dat, "
{name} [{start} -- {end}]{{.cvdate}}  
*{role}* at *{institution}*

- {notes}

	")
```

## Invited Presentations

### Local

Point-of-Care Ultrasound: Parasternal Long Axis [November 16, 2017]{.cvdate}  
*Division of General Medicine and Geriatrics*  
*Emory University School of Medicine*

The Problem Learner: A History and Physical for Learners with Difficulties [March 15, 2018]{.cvdate}  
*J. Willis Hurst Internal Medicine Residency Program*  
*Emory University School of Medicine*

The History of Sudden Cardiac Death: the Role of the Autonomic Nervous System [February 18, 2019]{.cvdate}  
*J. Willis Hurst Internal Medicine Residency Program*  
*Emory University School of Medicine*

- Senior Grand Rounds

Vagolysis and Arrhythmogenesis [February 12, 2023]{.cvdate}  
*University of Illinois Chicago Department of Medicine*

Autonomic and Structural Mechanisms in Atrial Fibrillation [December 18, 2023]{.cvdate}  
*University of Illinois Chicago Department of Medicine*

### Regional

"8 Minutes-to-Win-It": Top Inpatient Teaching Sessions by Soon-To-Be-Leaders [October 4, 2018]{.cvdate}  
*Southern Hospital Medicine Conference*

### National

Circadian Autonomic Inflexibility: A Marker of Ischemic Heart Disease [November 6, 2018]{.cvdate}  
*American Heart Association Scientific Sessions*

- Top Donors Meeting Presentation

ECG Prediction of Loss-of-Function *TTN* Variants [March 27, 2024]{.cvdate}  
*AFGen Consortium Fellowship Meeting*

Mendelian Randomization in Practice [April 24, 2024]{.cvdate}  
*AFGen Consortium Fellows Meeting*

## Funding

**NIH-T32 Postdoctoral Scholar** [2019 -- 2020]{.cvdate}  
*Disturbances of the Neurocardiac Axis: Using Heart Rate Variability to Measure Disease in the Brain and Heart*  
*NHLBI Training Grant*

- TL1-TR002382
- UL1-TR002378  

**NIH-T32 Postdoctoral Fellow** [2022 -- 2024]{.cvdate}  
*Training Program in Personalized Cardiovascular Medicine (TPIPCVM)*  
*NHLBI Training Grant*

- T32-HL139439

**NIH-F32 Principal Investigator** [2021 -- 2024]{.cvdate}
*Association of Autonomic Dysfunction with the Relationship between Depression and Coronary Disease*  
*NHLBI Training Grant*

- F32-HL154707

## Publications

### Peer-Reviewed Publications

```{r articles, results="asis"}
articles <-
  bib |>
  filter(type == "article-journal") |>
  mutate(numbers = case_when(
    !is.na(issue) ~ paste0(volume, "(", issue, ")", ", ", page),
    is.na(issue) ~ paste0(volume, ", ", page),
  ))

glue_data(articles, "1. {authors} ({year(date)}). {title}. {journal} {numbers}. doi:[{doi}](https://doi.org/{doi})")
```

### Working Manuscripts

```{r manuscripts, results="asis"}
manuscripts <-
  bib |>
  filter(type == "manuscript") |>
  filter(publisher == "draft")

glue_data(manuscripts, "1. {authors} ({year(date)}). {title}.")
```

### Research-In-Progress

```{r rip, results="asis"}
rip <-
  bib |>
  filter(type == "manuscript") |>
  filter(publisher == "rip")

glue_data(rip, "1. {authors} ({year(date)}). {title}.")
```

### Monographs

```{r thesis, results="asis"}
thesis <-
  bib |>
  filter(type == "thesis")

glue_data(thesis, "1. {authors} ({year(date)}). '{title}'. Master's Thesis. {publisher}. [{url}]({url})")
```

### Software

```{r software, results="asis"}
software <-
  bib |>
  filter(type == "software") |>
  # Fix formatting of titles
  mutate(
    title = sub("^Card", "card", title),
    title = sub("^Rmdl", "rmdl", title)
  )

glue_data(software, "1. {authors} ({year(date)}). {title}, Version: {version}. [{url}]({url})")
```

### Conference Proceedings

```{r abstracts, results="asis"}
abstracts <-
  bib |>
  filter(type == "paper-conference") |>
  mutate(numbers = case_when(
    !is.na(issue) ~ paste0(volume, "(", issue, ")", ", ", page),
    is.na(issue) ~ paste0(volume, ", ", page),
  ))

glue_data(abstracts, "1. {authors} ({year(date)}). {title}. {meeting}, {date}, {location}. In: {journal} {numbers}. doi:doi:[{doi}](https://doi.org/{doi})")
```
