---
name: Anish Sanjay Shah
date: "`r format(Sys.time(), '%B %D, %Y')`"
position: "Cardiology Fellow"
address: "Division of Cardiology, University of Illinois Chicago, Chicago, IL, 60607"
email: "ashah282@uic.edu"
phone: 773-222-5619
fax: 226-589-5000
www: asshah4.github.io
github: asshah4
twitter: shah_in_boots
output: 
  vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyr)
library(dplyr)
library(glue)
library(readr)

# All data
entries <- read_csv("entries.csv")
bib <- bibliography_entries("../bibliography/publications.bib")
```

Cardiology fellow with a clinical interest in neural regulation of cardiac physiology and cardiac electrophysiology, and a research interest in epidemiology/causality, harmonic regressions, recurrent event analysis, and digital signal processing. 

# Academic Qualifications and Positions

## Education

```{r education}
entries |>
	filter(section == "education") |>
	arrange(start) |>
	detailed_entries(
		when = glue("{start}--{end}"),
		what = title,
		with = institution,
		why = description
	) 
```

## Clinical Training

```{r training}
entries |>
	filter(section == "training") |>
	arrange(start) |>
	detailed_entries(
		when = glue("{start}--{end}"),
		what = title,
		with = institution,
		why = description
	) 
```

## Academic Appointments

```{r appts}
entries |>
	filter(section == "appointments") |>
	arrange(desc(start)) |>
	detailed_entries(
		when = glue("{start}--{end}"),
		what = title,
		with = institution,
		why = description
	) 
```

# Honors and Awards

```{r awards}
entries |>
	filter(section == "awards") |>
	arrange(desc(start)) |>
	detailed_entries(
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		),
		what = title,
		with = institution,
		why = description
	) 
```

# Professional Memberships

```{r soc}
entries |>
	filter(section == "societies") |>
	arrange(desc(start)) |>
	detailed_entries(
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		),
		what = title
	) 
```

# Teaching

## Teaching Positions

```{r teaching}
entries |>
	filter(section == "teaching") |>
	arrange(desc(start)) |>
	detailed_entries(
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		),
		what = title,
		with = institution,
		why = description
	) 
```

## Lectures

```{r talks}
entries |>
	filter(section == "talks") |>
	arrange(desc(start)) |>
	detailed_entries(
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		),
		what = title,
		with = institution,
		why = description
	) 
```

# Mentorship

## Students

```{r studs}
entries |>
	filter(section == "mentorship" & status == "student") |>
	detailed_entries(
		where = institution,
		why = description,
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		)
	)
```

## Residents

```{r resi}
entries |>
	filter(section == "mentorship" & status == "resident") |>
	detailed_entries(
		where = institution,
		why = description,
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		)
	)
```

## Research

```{r research}
entries |>
	filter(section == "mentorship" & status == "research") |>
	detailed_entries(
		where = institution,
		why = description,
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		)
	)
```

# Skills 

```{r lang}
entries |>
	filter(section == "skills") |>
	detailed_entries(
		what = title,
		why = description
	) 
```

# Certifications

## Professional

```{r pro certs}
entries |>
	filter(section == "certifications" & status == "professional") |>
	detailed_entries(
		what = title,
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		)
	)
```

## Personal

```{r per certs}
entries |>
	filter(section == "certifications" & status == "personal") |>
	detailed_entries(
		what = title,
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		)
	)
```

# Research

## Grant Funding

```{r}
entries |>
	filter(section == "grants") |>
	arrange(desc(start)) |>
	detailed_entries(
		when = case_when(
			is.na(end) ~ glue("{start}"),
			!is.na(end) ~ glue("{start}--{end}")
		),
		what = title,
		where = location,
		with = institution,
		why = description
	)
```

## Conferences

```{r conferences}
bib |>
	filter(type == "paper-conference") |>
	arrange(issued) |>
	select(-c(volume, issued, abstract, URL, DOI, ISSN, page, keyword, PMID))
```

## Software

```{r packages}
bib |>
	filter(type == "no-type") |>
	arrange(issued) |>
	select(-c(volume, issued, abstract, DOI, ISSN, page, keyword, PMID, `container-title`))
```

## Publications

```{r pubs}
bib |>
	filter(type == "article-journal") |>
	arrange(issued) |>
	select(-c(issued, ISSN, publisher, page, keyword, PMID))
```
